---
title: "FatherSonDataset"
author: "Dooratharsini Paskaran"
date: '2022-06-21'
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```



## Exploratory Data Analysis

- This is an R Markdown presentation created as a part of Coursera DataScience Specialization : Developing Data Products Course.

- Selected father son Data set from "UsingR" Package. 

- The dataset contains height of 1078 fathers and their corresponding sons in inches. 

- A data set contains 1078 observations on following 2 variables.

fheight - Father's height in inches

sheight - Son's height in inches

```{r, echo=FALSE,results='hide',warning=FALSE,message=FALSE}
library(UsingR)
data(father.son)

```

```{r}
str(father.son)
```

```{r}
head(father.son)
```

- Few lines from data set

## Liner Model

- There seems to be an association between heights of fathers and those of sons. 

- As you can see, as the height of father increases, those of son also increase. The strength of the association is calculated through correlation.

```{r, echo=TRUE}
cor(father.son)
```

- Analysis will establish a linear relation between height of father and son.

- Through a linear regression model, the height of son is predicted by height of father's.

## Building linear model and Prediction
### Building Model
```{r, echo=FALSE}
fit <- lm(father.son$sheight~father.son$fheight)
```
```{r, echo=TRUE}
summary(fit)
```
 
### Prediction

- Linear relationship is established between height of father and son. 
- Using the equation, height of the sons can be predicted by the height of their fathers. 


## Plot

```{r}
plot(father.son$fheight, father.son$sheight, xlab = "Father's Height", ylab = "Son's Height")
abline(fit,lwd=2,col="blue")
title(main="Height of father's Vs. Height of son's")
```

Height of the fathers and sons are associated positively with each other. As the height of father increases,those of sons also increase.
